### 2016-11-08 R/ITHIM.Rmd
Edits to Materials & Methods

>>>>

## Non-Travel METs

```{r newMETs, echo = TRUE, eval = FALSE, echo = FALSE}
newMETsFile <- "ATUS_to_METS_key.csv"

newMETsFile <- system.file(newMETsFile, package="ITHIM")

newMETs <- read.csv(file = newMETsFile, stringsAsFactors = FALSE, colClasses = c("character","character","character","character","numeric","character","character","character"))
dataColumns <- c(1,5)
D <- newMETs[,dataColumns]
metaData <- newMETs[,-dataColumns]
newMETs <- list(Data = D, metaData = metaData)
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))

rownames(newMETs$Data) <- activityCode
rownames(newMETs$metaData) <- activityCode

newMETs$metaData <- within(newMETs$metaData, {
  Travel.related..Y.N. <- as.factor(Travel.related..Y.N.)
})

metKey <- newMETs$Data$AinsworthMETS
names(metKey) <- activityCode

```{r readnewMETs, echo = TRUE, eval = FALSE, echo = FALSE}
cpsFile <- "~/GHI/data/ATUS/atuscps_2015.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

summaryFile <- "~/GHI/data/ATUS/atussum_2015.dat"
summary <- read.table(summaryFile, header=T, skip=0, sep=",")
metaDataColumns <- 1:24
summaryList <- list(Data = summary[,-metaDataColumns], metaData = summary[,metaDataColumns])

summaryList$metaData <- within(summaryList$metaData,{
    TESEX <- as.factor(ifelse(TESEX == 1, "male", ifelse(TESEX == 2, "female",NA)))
    AGECAT <- ifelse(TEAGE <5, "00-04",
                     ifelse(TEAGE > 4 & TEAGE < 15, "05-14",
                     ifelse(TEAGE > 14 & TEAGE < 30, "15-29",
                     ifelse(TEAGE > 29 & TEAGE < 45, "30-44",
                     ifelse(TEAGE > 44 & TEAGE < 60, "45-59",
                     ifelse(TEAGE > 59 & TEAGE < 70, "60-69",
                     ifelse(TEAGE > 69 & TEAGE < 80, "70-79", "80+"
                            )))))))})

We shift the MET estimates by the minimum value so that the new minimum MET estimate is zero.

```{r metKey, echo = TRUE, eval = FALSE, echo = FALSE}
allActivities <- colnames(summaryList$Data)
nonTravelActivities <- rownames(newMETs$metaData)[which(newMETs$metaData$Travel.related..Y.N. == "N")]
nonTravelActivities <- nonTravelActivities[which(nonTravelActivities %in% allActivities)]

activities <- nonTravelActivities

metKeyVector <- (metKey[activities] - min(metKey, na.rm = TRUE))/60*7
names(metKeyVector) <- activities
metKeyMatrix <- matrix(metKeyVector, nrow = nrow(summaryList$Data), ncol = length(metKeyVector), byrow = TRUE)
dimnames(metKeyMatrix) <- list( NULL, activities)

METs <- data.frame(METs = rowSums(summaryList$Data[,activities] * metKeyMatrix[,activities], na.rm = TRUE), AGE = summaryList$metaData$TEAGE, SEX = summaryList$metaData$TESEX, AGECAT = summaryList$metaData$AGECAT, row.names = summaryList$metaData$TUCASEID )

D <- merge(cps, METs, by.y = "row.names", by.x = "TUCASEID")
ggplot(D, aes(x = METs, ..density.., colour = AGECAT)) + geom_freqpoly(binwidth = 10) + facet_grid( SEX ~ .) + labs(x = "Non-Travel Marginal MET-hrs./week", colour = "Age") + coord_cartesian(xlim = c(0, 400))

```{r parameters, eval = FALSE, echo = FALSE}
parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             )

(METmatrix <- rbind(matrix(0,nrow = 2, ncol = 2), matrix(parameters$mean, ncol = 2)))

colnames(METmatrix) <- c(as.character(parameters$SEX[1]),as.character(rev(parameters$SEX)[1]))

METmatrix <- METmatrix[,c("male","female")]

METmatrix <- METmatrix/METmatrix[3,2]
